Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2024-06-19 paper/paper.tex
Update paper.tex

\begin{minipage}{\linewidth}
\begin{lstlisting}[language = Julia, caption={Juila interface MPI conversion.}]
\\ OpenMPI
Jcomm = MPI.Comm(ccall((:MPI_Comm_f2c, \
        "openmpi/lib/libmpi.so"),Ptr{Cvoid}, \
        (Cint,),Cint(Jcomm)))

\\ MPICH and MVAPICH
Jcomm = MPI.Comm(Cint(Jcomm))
\end{lstlisting}
\end{minipage}

>>>>

\begin{minipage}{\linewidth}
\begin{lstlisting}[language = Julia, caption={Juila interface MPI conversion.}]
// OpenMPI
Jcomm = MPI.Comm(ccall((:MPI_Comm_f2c, \
        "openmpi/lib/libmpi.so"),Ptr{Cvoid}, \
        (Cint,),Cint(Jcomm)))

// MPICH and MVAPICH
Jcomm = MPI.Comm(Cint(Jcomm))
\end{lstlisting}
\end{minipage}
